---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The Early Career Researcher Tool Box

This tool box aims at helping ECR going to big conferences for the first time.
It contains:

- a tutorial to make a CV webpage with a downloadable pdf version.
- a script to make a QR code directing to your webpage
- a conference bingo, what you should aim for when going to conferences

## CV as a github page

Making your CV as a github page has several advantages.
It is easy to update, it is always available, and list of publications can be automated.
The idea is to create the CV as a quarto document, that will be rendered both in pdf and html.
The pdf version having a button to download it from the html one.
Setting up a github action, we can publish the new version of the webpage automatically everytime a change is pushed to the main branch.

### Acknowledgement

The idea of making a webpage CV that would also be rendered in pdf was first described in [this article from Cynthia Huang](https://www.cynthiahqy.com/posts/cv-html-pdf/).
The handling of lists of publications and mobile view has been added to the original tutorial.


### Short biography
The "no-print" box allows you to have a short text that appears on the webpage version but not in the pdf.
This can be modified in the css file.


### Contact infos on mobile
For some reasons, when rendering a quarto file into an html, the table of content and contact informations does not appear on the mobile version.
This is a massive issue, because in conferences most people will access your page throuhg a smartphone.
The "hide-on-desktop" block allows you to add information that will not appear on a screen larger than 481px.
This can be changed in the css file.


### Lists of publications
You can have several lists of publications: peer reviewed articles, popular science, books, and what not.
Each list of publication needs to be in a separated bib file.
The trick is to use the `multibib` filter, `nocite` to list publication that are not cited, and `validate-yaml: false` to silence an unwanted error.
You will need to install the multibib filter from its [github repo](https://github.com/pandoc-ext/multibib#readme).
The style of the publication lists depend on the csl (citation style language) file.
Different csl can be downloaded on the [Zotero Style Repository](https://www.zotero.org/styles).


### Rendering

You need to first install weasyprint, instruction can be found on [this page](https://doc.courtbouillon.org/weasyprint/stable/first_steps.html#installation).

Then run this code to render:

```{r, eval = FALSE}
quarto::quarto_render("index.qmd", output_format = "all")
```

### Making a github page

Now we want to make a github page, and we want the page to update everytime we pull an update in the main branch.
That way, you can update your CV on another branch, and when it looks nice you open a pull request and it updates the webpage.
Side note: you can have the github repo as private and the page as public, showing only your nicest side.

The full documentation to setup a github actiona can be found in the [github documentation](https://docs.github.com/en/pages/getting-started-with-github-pages/configuring-a-publishing-source-for-your-github-pages-site#publishing-with-a-custom-github-actions-workflow)

In short:

- go on your github repo, under settings > pages
- as source, select "GitHub Actions"
- choose "static HTML"
- commit the changes to the main branch


## Making a QR code R

```{r, eval = FALSE}
qrcode <- qr_code("webpage")
generate_svg(qrcode, filename = "qrcode.svg")
plot(qrcode)
```

## Conference bingo

Time to play with your colleagues!

Print this bingo, pack it and try to not yell BINGO too loud in the middle of a session.

|     Asked a question (oral presentation)    |                  Had lunch with newly met people                  | Explored the  nature/culture/etc of the conference location |          Solved a science problem or puzzle I've been struggling with          |   |
|              Exchanged contacts             |                     Asked a question (poster)                     |       Went to a skills devellopment course or workshop      | Made action points for yourself about things to follow up after the conference |   |
|           Got a new research idea           |                 Listened to a talk out of my field                |                 Asked a question (any setup)                |                         Introduced myself and my topic                         |   |
| Went to a society or interest group meeting | Picked up a cool / useful new skill of relevance for my research  |           Had a coffee or drink with a new person           |                  Shared an outstanding finding with colleagues                 |   |

