---
output: github_document
bibliography: /home/jga051/Dropbox/PhD/biblio_phd_zot.bib
csl: /home/jga051/Documents/01_PhD/emerald-harvard.csl
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# A Tool Box for Early Career Researchers going to big conferences

This tool box aims at helping ECR going to big conferences for the first time.
It contains:

- a tutorial to make a CV webpage with a downloadable pdf version.
- a script to make a QR code directing to your webpage
- a conference bingo, what you should aim for when going to conferences

Feel free to suggest content (via a github issue ideally) or fork it and adapt it as you please.

## CV as a github page

Making your CV as a github page has several advantages:

- It is easy to update and maintain.
  My trick is to put everything in the working file, and pass as comments what I currently do not want to show.
- It is always available, as long as there is internet, which is great for networking.
- Lists of publicatons are easier to handle
- It looks cool (I might be biased on that one).

The idea is to create the CV as a quarto document, that will be rendered both in pdf and html.
Then we create a github page to host the html version, with a button on the page to download the pdf version.
Setting up a github action, we can publish the new version of the webpage automatically everytime a change is pushed to the main branch.
See the example [here](https://jogaudard.github.io/ecr_toolbox/).

### Acknowledgement

The idea of making a webpage CV that would also be rendered in pdf was first described in [this article from Cynthia Huang](https://www.cynthiahqy.com/posts/cv-html-pdf/) [@huang2023].
The handling of lists of publications, mobile view, and github page automation have been added to the original tutorial.

### Getting started

Generate a new repository from this template, gather your degrees and publications, and let's get started!
For a basic use, you will only need to edit the `index.qmd` (that is the CV itself), the files in the `publications` folder, and the QR code code chunk.
If you wish to modify the layout, you will need to modify `cv.css` as well.
In the `index.qmd`, you need to fill in your own information in the yaml and the short biography, and add the sections you need.
Bibliographies will be done using bibtex (see below).


### Short biography
The "no-print" box allows you to have a short text that appears on the webpage version but not in the pdf.
This can be modified in the css file.


### Contact infos on mobile
For some reasons, when rendering a quarto file into an html, the table of content and contact informations does not appear on the mobile version.
This is a massive issue, because in conferences most people will access your page using a smartphone.
The "hide-on-desktop" block allows you to add information that will not appear on a screen larger than 481px.
This can be changed in the css file.


### Lists of publications
You can have several lists of publications: peer reviewed articles, popular science, books, R packages, and what not.
Each list of publication needs to be in a separated bib file, that you call in the yaml.
You change the citation style by changing the citation style language file (csl).
Different csl can be downloaded on the [Zotero Style Repository](https://www.zotero.org/styles).
Change the `bold-auth-name:` in the yaml to have your name appear in bold.
And for publication with many authors where your name does not appear, the trick is to manually change the entry in the bib file to get your name higher in the list.

All of this works with the [multibib](https://github.com/pandoc-ext/multibib#readme) and [bold-author](https://stackoverflow.com/a/76429867/10685715) extensions, in case you want to dive deeper.


### Rendering

You need to first install weasyprint, instruction can be found on [this page](https://doc.courtbouillon.org/weasyprint/stable/first_steps.html#installation).

Then run this code to render:

```{r, eval = FALSE}
quarto::quarto_render("index.qmd", output_format = "all")
```

### Making a github page

Now we want to make a github page, and we want the page to update everytime we pull an update in the main branch.
That way, you can update your CV on another branch, and when it looks nice you open a pull request and it updates the webpage.
Side note: you can have the github repo as private and the page as public, showing only your nicest side.

The full documentation to setup a github action can be found in the [github documentation](https://docs.github.com/en/pages/getting-started-with-github-pages/configuring-a-publishing-source-for-your-github-pages-site#publishing-with-a-custom-github-actions-workflow)

In short:

- go on your github repo, under settings > pages
- as source, select "GitHub Actions"
- choose "static HTML"
- commit the changes to the main branch

Your CV is now online with an address that looks like this: [username.github.io/[cv_repo_name]](https://jogaudard.github.io/ecr_toolbox/)!

## Making a QR code in R

QR codes are great.
You can print them as stickers and have them at the back of your phone for example.
And when someone asks how to stay in touch, or about your work, just hand it to them to scan.

BUT... most "free" QR code generators are collecting data about the people scanning your QR code.
Not cool.
The `qrcode` package [@onkelinxQrcodeGenerateQrcodes2024] in R does not do that.

```{r, eval = FALSE}
library(qrcode)
qrcode <- qr_code("webpage")
generate_svg(qrcode, filename = "qrcode.svg")
plot(qrcode)
```

## Conference bingo

Time to play with your colleagues!

Print this bingo, pack it and try to not yell BINGO too loud in the middle of a session.

 --------------------------------------------- ------------------------------------------------------------------ -------------------------------------------------------------- --------------------------------------------------------------- -------------------------------------------------------------------------------
      Asked a question (oral presentation)                       Had lunch with newly met people                    Explored the  nature/culture/etc of the conference location    Solved a science problem or puzzle I've been struggling with                                   Helped someone                                  
         Exchanged contact information                              Asked a question (poster)                             Went to a skills devellopment course or workshop        Attended a presentation or workshop around inclusivity topics   Made action points for yourself about things to follow up after the conference  
    Met with a former colleague / supervisor                    Listened to a talk out of my field                                  Asked a question (any setup)                                  Introduced myself and my topic                                              Got a new research idea                             
  Went to a society or interest group meeting   Picked up a cool / useful new skill of relevance for my research              Had a coffee or drink with a new person                     Shared an outstanding finding with colleagues                       Attended a presentation or workshop about mental health             
 --------------------------------------------- ------------------------------------------------------------------ -------------------------------------------------------------- --------------------------------------------------------------- -------------------------------------------------------------------------------


 <!-- --------------------------------------------- ------------------------------------------------------------------- ------------------------------------------------------------- -------------------------------------------------------------------------------- 
      Asked a question (oral presentation)                       Had lunch with newly met people                    Explored the  nature/culture/etc of the conference location            Solved a science problem or puzzle I've been struggling with           
               Exchanged contacts                                   Asked a question (poster)                             Went to a skills devellopment course or workshop        Made action points for yourself about things to follow up after the conference  
            Got a new research idea                             Listened to a talk out of my field                                  Asked a question (any setup)                                          Introduced myself and my topic                          
  Went to a society or interest group meeting   Picked up a cool / useful new skill of relevance for my research              Had a coffee or drink with a new person                              Shared an outstanding finding with colleagues                  
 --------------------------------------------- ------------------------------------------------------------------- ------------------------------------------------------------- --------------------------------------------------------------------------------  -->

## Conference DOs

- Have a couple of A4 prints of your poster with you at all times.
- Have your slides on your phone (true story: I redid my presentation to some important people who had missed it on the U1 in Vienna at 23:00 from my phone slides.)
- Reach out to your network (former supervisor, people met on a course, ...) before the conference and get organised to meet.
- Use your university email. Most big conferences have a tool to find people with their email.
- Take it easy, escape once in a while, do sports (or whatever provides you balance).

<!-- ## Conference DON'Ts -->

### References
